Work Fragmentation in Developer Interaction Data

### 2015-08-09 paper.tex
cambio de tamaño de graficas

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=1.0\linewidth,clip=, angle=0]{figures/hist_rejected} 
\end{tabular}
\caption{Grouping by date all the traces, with aggregate information (light gray) and without aggregate information (dark gray).}
\label{fig:hist_rejected}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{tabular}{c}
\includegraphics[width=0.75\linewidth,clip=, angle=0]{figures/mass_event} 
\end{tabular}
\caption{Replacing five massive events with only two events.}
\label{fig:mass_event}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{prevalence of interruptions according to their duration time. }
\label{tbl:by_duration}
\centering
\begin{tabular}{p{2.1cm}|p{0.8cm}|p{3.4cm}} 
duration & ratio & examples  \\
  \hline   
$[3  - 12 min \rangle$ & 69\% & short pause, answer a question, thinking, looking for interruption  \\ 
\hline 
$[12  - 30 min \rangle$ & 18\% & coffee break, short meeting, extended interruption  \\
$[30 min - 2 hr \rangle$  & 9\% & lunch break, a meeting  \\
$[2 hr - 8 hr \rangle$ & 4\% & extended meeting \\
%$[8 hr - \infty \rangle$ & 0.14 & \textit{a long interruption}   \\
%$[8 hr -  \infty \rangle$ & 0.06  &  a weekend \\
%$[2 day - \infty \rangle$ & 0.04 & a long holiday \\ 
\end{tabular}
\end{table}

@@

\begin{figure}[t]
\centering
\begin{tabular}{c}
\includegraphics[width=.95\linewidth,clip=, angle=0]{figures/trans} 
\end{tabular}
\caption{Example of how to compress a time series. }
\label{fig:trans}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/box_int_events_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/box_int_events_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/box_int_ratio} \\
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selection events per minute, the edit ratio, and the number of interruptions. }
\label{fig:box_int_events}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Effect size and significance of the relationship between number of edit per minute, selection per minute, edit ratio, and number of interruptions} 
\label{tbl:p_value}
\centering
\begin{tabular}{l | p{0.75cm} | p{0.85cm} | p{0.85cm} | p{0.85cm} |p{0.75cm}}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/box_plot_range_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/box_plot_range_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/box_dur_ratio}
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration}
\label{fig:box_dur_events}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/without_int_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/with_int1_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/with_int2_med} 
\end{tabular}
\caption{Global representation of a session with: no interruptions (top); only short interruptions (middle); and at least one prolonged interruption (bottom). }
\label{fig:bins_int}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.9\linewidth,clip=, angle=0]{figures/all_ints} 
\end{tabular}
\caption{Local effect of an interruption in the user activity.}
\label{fig:all_ints}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.9\linewidth,clip=, angle=0]{figures/ratio_all} 
\end{tabular}
\caption{Ratio of edits around the interruption. }
\label{fig:ratio_all}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
Positive Effect \\
\includegraphics[width=0.9\linewidth,clip=, angle=0]{figures/ratio_pos} \\ 
\\
Negative Effect \\
\includegraphics[width=0.9\linewidth,clip=, angle=0]{figures/ratio_neg} \\
\end{tabular}
\caption{Ratio of edits for positive and negative local effect. }
\label{fig:ratio_rest}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Attributes in UDC data. }
\label{tbl:att_udc}
\centering
\begin{tabular}{|p{1.7cm}|p{3.5cm}|} 
  \hline 
attribute & description \\  
  \hline 
    \hline 
userId &  Unique number that identifies a user \\
what & The action of the event (deactivated, activated, opened, executed, etc.)  \\
kind & What kind of event was executed (workbench, view, command, etc.)  \\
bundleId & Description of the event's package  \\
bundleVersion & Version of the bundle's event  \\
description & Description of the event\\
datetime & Date and time in UNIX format\\
  \hline
\end{tabular}

@@

Thus, by default, all events of the attributes \textit{command} and \textit{executed} were classified as edition and afterwards we did a thorough analysis to identify those that are actually selection events.  This way we categorized as selection all the events where we could tell based on the description if they have the purpose to, for instance, navigate to another window, open a perspective, find and replace words, search code, debug code, or perform window management. The description contains the whole path from the top package to the class that implements the event, so we look for key words to apply the classification. The proportion of events after the classification is shown in the table \ref{tbl:prop_events_udc}.
We used an iterative process involving two of the authors of the paper to arrive to this result; the process was iterative, until we reached consensus.

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Proportion of events. }
\label{tbl:prop_events_udc}
\centering
\begin{tabular}{|p{1.7cm}|p{2 cm}|} 
  \hline 
event & percentage \\  
  \hline 
    \hline 
edition &  $34.6\%$  \\
selection & $31.1\%$ \\
system & $31.5\%$  \\
control & $0.8\%$  \\
\hline
\end{tabular}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_int_events_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_int_events_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_int_events_ratio} \\
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selection events per minute, the edit ratio, and the number of interruptions. }
\label{fig:box_int_events_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_plot_range_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_plot_range_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_dur_ratio}
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration}
\label{fig:box_dur_events_udc}
\end{figure}

@@

\subsection{RQ3: Local relationships between interruptions and productivity}
The sessions with UDC went through the same process of transformation into 10 chunks of equal time. The results on the Figure \ref{fig:bins_int_udc} shows similar, but not identical patterns compared to the ones we observed in Mylyn.
\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_without_int_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_with_int1_med} \\
\includegraphics[width=.80\linewidth,clip=, angle=0]{figures/udc_with_int2_med} 
\end{tabular}
\caption{Global representation of a session with: no interruptions (top); only short interruptions (middle); and at least one prolonged interruption (bottom). }
\label{fig:bins_int_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.9\linewidth,clip=, angle=0]{figures/udc_all_ints} 
\end{tabular}
\caption{Local effect of an interruption in the user activity.}
\label{fig:all_ints_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_recovery_edit}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_recovery_sel}  \\
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_recovery_ratio} \\
\end{tabular}
\caption{Boxplots showing the detailed evolution of editions, selections and edit ratio during recovery time and after recovery time. }
\label{fig:box_recovery_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.8\linewidth,clip=, angle=0]{figures/udc_box_recovery_pos_ratio} \\
\end{tabular}
\caption{Boxplot of the edit ratio during recovery time after a positive or negative interruption, compared to the edit ratio overall. }
\label{fig:box_recovery_effect_udc}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{New category of events. }
\label{tbl:new_events_udc}
\centering
\begin{tabular}{|p{1.7cm}|p{4 cm}|} 
  \hline 
category & description \\  
  \hline 
    \hline 
clean-build &  Events related to the build sysem (clean, build or run a project) \\
control & Version events events \\
debug & Events executed during debugging sessions  \\
edit-text & Text edition events  \\
file & Management of files (saving, closing, opening, etc.)  \\
find-replace & Search and replacement of text  or code entities \\
high-nav & High-level navigation through classes, windows and artifacts \\
perspective & Change of perspectives in Eclipse  \\
refactoring & Refactoring events \\
search & Text or code search  \\
text-nav & Low-level text navigation \\

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Comparison of execution after positive or negative interruptions. }
\label{tbl:stats_events}
\centering
\begin{tabular}{|p{1.7cm}|p{1cm} |p{1cm}|p{1cm}|} 
  \hline 
category & positive & negative & all \\  
  \hline 
    \hline 
edit-text &  \textbf{79.43} & 51.71 & 61.00 \\
file &  \textbf{51.83} & 49.14 & 48.42\\
refactoring & \textbf{0.62} & 0.41 & 0.52 \\
high-nav & 25.77 & \textbf{32.20} & 26.70  \\
find-replace & 7.64 & \textbf{9.24} & 7.01 \\
debug & 2.09 & \textbf{5.69} & 5.53  \\
search & 2.63 & \textbf{4.29} & 3.33 \\
clean-build & 0.59 & \textbf{0.83} & 0.76  \\
text-nav & 24.31 & 21.79 & \textbf{25.78} \\
perspective & 3.41 & 4.96 & \textbf{6.31}  \\
control & 0.58 & 0.89 & \textbf{0.90} \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.5\linewidth,clip=, angle=0]{figures/hist_rejected} 
\end{tabular}
\caption{Grouping by date all the traces, with aggregate information (light gray) and without aggregate information (dark gray).}
\label{fig:hist_rejected}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{tabular}{c}
\includegraphics[width=0.5\linewidth,clip=, angle=0]{figures/mass_event} 
\end{tabular}
\caption{Replacing five massive events with only two events.}
\label{fig:mass_event}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{prevalence of interruptions according to their duration time. }
\label{tbl:by_duration}
\centering
\begin{tabular}{p{3cm}|p{0.8cm}|p{4cm}} 
duration & ratio & examples  \\
  \hline   
$[3  - 12 min \rangle$ & 69\% & short pause, answer a question, thinking, looking for interruption  \\ 
\hline 
$[12  - 30 min \rangle$ & 18\% & coffee break, short meeting, extended interruption  \\
$[30 min - 2 hr \rangle$  & 9\% & lunch break, a meeting  \\
$[2 hr - 8 hr \rangle$ & 4\% & extended meeting \\
%$[8 hr - \infty \rangle$ & 0.14 & \textit{a long interruption}   \\
%$[8 hr -  \infty \rangle$ & 0.06  &  a weekend \\
%$[2 day - \infty \rangle$ & 0.04 & a long holiday \\ 
\end{tabular}
\end{table}

@@

\begin{figure}[t]
\centering
\begin{tabular}{c}
\includegraphics[width=.5\linewidth,clip=, angle=0]{figures/trans} 
\end{tabular}
\caption{Example of how to compress a time series. }
\label{fig:trans}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_int_events_edit}  
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_int_events_sel}  
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_int_ratio} 
\endminipage\hfill
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selection events per minute, the edit ratio, and the number of interruptions. }
\label{fig:box_int_events}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Effect size and significance of the relationship between number of edit per minute, selection per minute, edit ratio, and number of interruptions} 
\label{tbl:p_value}
\centering
\begin{tabular}{l | p{0.75cm} | p{1.2cm} | p{1.2cm} | p{1.2cm} |p{1.2cm}}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_plot_range_edit}  
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_plot_range_sel}  
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_dur_ratio}
\endminipage\hfill
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration}
\label{fig:box_dur_events}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/without_int_med} 
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/with_int1_med} 
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/with_int2_med} 
\endminipage\hfill
\end{tabular}
\caption{Global representation of a session with: no interruptions (top); only short interruptions (middle); and at least one prolonged interruption (bottom). }
\label{fig:bins_int}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.5\linewidth,clip=, angle=0]{figures/all_ints} 
\end{tabular}
\caption{Local effect of an interruption in the user activity.}
\label{fig:all_ints}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.5\linewidth,clip=, angle=0]{figures/ratio_all} 
\end{tabular}
\caption{Ratio of edits around the interruption. }
\label{fig:ratio_all}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.5\textwidth}
\begin{center}
{Positive Effect}
\end{center} 
\includegraphics[width=\linewidth,clip=, angle=0]{figures/ratio_pos} \\

\endminipage\hfill
\minipage{0.5\textwidth}
\begin{center}
Negative Effect
\end{center}

\includegraphics[width=\linewidth,clip=, angle=0]{figures/ratio_neg} \\
\endminipage\hfill
\end{tabular}
\caption{Ratio of edits for positive and negative local effect. }
\label{fig:ratio_rest}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Attributes in UDC data. }
\label{tbl:att_udc}
\centering
\begin{tabular}{|p{2.5cm}|p{7cm}|} 
  \hline 
attribute & description \\  
  \hline 
    \hline 
userId &  Unique number that identifies a user \\
what & The action of the event (deactivated, activated, opened, executed, etc.)  \\
kind & What kind of event was executed (workbench, view, command, etc.)  \\
bundleId & Description of the event's package  \\
bundleVersion & Version of the bundle's event  \\
description & Description of the event\\
datetime & Date and time in UNIX format\\
  \hline
\end{tabular}

@@

Thus, by default, all events of the attributes \textit{command} and \textit{executed} were classified as edition and afterwards we did a thorough analysis to identify those that are actually selection events.  This way we categorized as selection all the events where we could tell based on the description if they have the purpose to, for instance, navigate to another window, open a perspective, find and replace words, search code, debug code, or perform window management. The description contains the whole path from the top package to the class that implements the event, so we look for key words to apply the classification. The proportion of events after the classification is shown in the table \ref{tbl:prop_events_udc}.
We used an iterative process involving two of the authors of the paper to arrive to this result; the process was iterative, until we reached consensus. A sample of the classification can be seen on the Table \ref{tbl:ej_events_udc}.

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Proportion of events. }
\label{tbl:prop_events_udc}
\centering
\begin{tabular}{|p{1.7cm}|p{2 cm}|} 
  \hline 
event & percentage \\  
  \hline 
    \hline 
edition &  $34.6\%$  \\
selection & $31.1\%$ \\
system & $31.5\%$  \\
control & $0.8\%$  \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Sample of classified events. }
\label{tbl:ej_events_udc}
\centering
\begin{tabular}{|p{7.5cm}| p{2 cm} |} 
  \hline 
description & type \\  
  \hline 
    \hline 
org.eclipse.ui.edit.delete & edition \\
org.eclipse.ui.file.save & edition \\
org.eclipse.ui.edit.undo & edition \\
org.eclipse.jdt.ui.CompilationUnitEditor & selection \\
org.eclipse.ui.console.ConsoleView & selection \\
org.eclipse.debug.ui.commands.StepOver & selection \\ 
org.eclipse.ui.workbench & system \\
org.eclipse.team.sync.views.SynchronizeView & control \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_int_events_edit}  \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_int_events_sel}  \\
\endminipage\hfil
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_int_events_ratio} \\
\endminipage\hfill
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selection events per minute, the edit ratio, and the number of interruptions. }
\label{fig:box_int_events_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_plot_range_edit}  \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_plot_range_sel}  \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_dur_ratio} \\
\endminipage\hfill
\end{tabular}
\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration}
\label{fig:box_dur_events_udc}
\end{figure}

@@

\subsection{RQ3: Local relationships between interruptions and productivity}
The sessions with UDC went through the same process of transformation into 10 chunks of equal time. The results on the Figure \ref{fig:bins_int_udc} shows similar, but not identical patterns compared to the ones we observed in Mylyn.

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_without_int_med} \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_with_int1_med} \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_with_int2_med} \\
\endminipage\hfill
\end{tabular}
\caption{Global representation of a session with: no interruptions (top); only short interruptions (middle); and at least one prolonged interruption (bottom). }
\label{fig:bins_int_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=0.5\linewidth,clip=, angle=0]{figures/udc_all_ints} 
\end{tabular}
\caption{Local effect of an interruption in the user activity.}
\label{fig:all_ints_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_recovery_edit}  \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_recovery_sel}  \\
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_recovery_ratio} \\
\endminipage\hfill
\end{tabular}
\caption{Boxplots showing the detailed evolution of editions, selections and edit ratio during recovery time and after recovery time. }
\label{fig:box_recovery_udc}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{c}
\includegraphics[width=.5\linewidth,clip=, angle=0]{figures/udc_box_recovery_pos_ratio} \\
\end{tabular}
\caption{Boxplot of the edit ratio during recovery time after a positive or negative interruption, compared to the edit ratio overall. }
\label{fig:box_recovery_effect_udc}
\end{figure}

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{New category of events. }
\label{tbl:new_events_udc}
\centering
\begin{tabular}{|p{2.5cm}|p{9 cm}|} 
  \hline 
category & description \\  
  \hline 
    \hline 
clean-build &  Events related to the build sysem (clean, build or run a project) \\
control & Version events events \\
debug & Events executed during debugging sessions  \\
edit-text & Text edition events  \\
file & Management of files (saving, closing, opening, etc.)  \\
find-replace & Search and replacement of text  or code entities \\
high-nav & High-level navigation through classes, windows and artifacts \\
perspective & Change of perspectives in Eclipse  \\
refactoring & Refactoring events \\
search & Text or code search  \\
text-nav & Low-level text navigation \\

@@

\begin{table}[ht!]
\renewcommand{\arraystretch}{1.3}
\caption{Comparison of execution after positive or negative interruptions. }
\label{tbl:stats_events}
\centering
\begin{tabular}{|p{3cm}|p{1cm} |p{1cm}|p{1cm}|} 
  \hline 
category & positive & negative & all \\  
  \hline 
    \hline 
edit-text &  \textbf{79.43} & 51.71 & 61.00 \\
file &  \textbf{51.83} & 49.14 & 48.42\\
refactoring & \textbf{0.62} & 0.41 & 0.52 \\
high-nav & 25.77 & \textbf{32.20} & 26.70  \\
find-replace & 7.64 & \textbf{9.24} & 7.01 \\
debug & 2.09 & \textbf{5.69} & 5.53  \\
search & 2.63 & \textbf{4.29} & 3.33 \\
clean-build & 0.59 & \textbf{0.83} & 0.76  \\
text-nav & 24.31 & 21.79 & \textbf{25.78} \\
perspective & 3.41 & 4.96 & \textbf{6.31}  \\
control & 0.58 & 0.89 & \textbf{0.90} \\
\hline
\end{tabular}
\end{table}
